Uncertainty-aware graph-based multimodal remote sensing classification

### 2021-06-25 latex/IEEE/bare_jrnl.tex
Moved latex into designated dir

\subsection{Subjective Logic}
In order to understand the mapping between Dirichlet distributions and uncertainty estimates, it is first necessary to describe the Subjective Logic (SL) framework. The uncertainty reasoning described by SL takes an evidence-based approach to decision making \cite{DBLP:books/sp/Josang16}. Expressing an opinion using measured quantities of belief allows the distinction to be made between uncertainty due to a lack of evidence (vacuity) or uncertainty due to the presence of conflicting evidence (dissonance). A multinomial opinion, $\omega$, can be expressed as $\omega=\left(\mathbf{b}, u, \mathbf{a}\right)$, where $\mathbf{b}$ is a belief mass vector, the scalar $u$ is the uncertainty mass and $\mathbf{a}$ is the base rate vector. For an output, $\mathbf{y}$, of dimension K
\begin{equation}
    \mathbf{b}\in\mathbb{R}^K,\quad\mathbf{a}\in\mathbb{R}^K,\quad\mathbf{y}\in\mathbb{R}^K.
\end{equation}
A projection of $\omega$ onto a probability distribution can be made according to
\begin{equation}
    P(y=k) = b_k + a_ku.
\label{eq:prob_projection}
\end{equation}
Given that for the base rate vector $\sum_{k=1}^Ka_k=1$, an additivity requirement is described by
\begin{equation}
    u+\sum_{k=1}^K b_k=1.
\end{equation}

>>>>

\subsection{Subjective Logic}

In order to understand the mapping between Dirichlet distributions and uncertainty estimates, it is first necessary to describe the Subjective Logic (SL) framework. The uncertainty reasoning described by SL takes an evidence-based approach to decision making \cite{DBLP:books/sp/Josang16}. Expressing an opinion using measured quantities of belief allows the distinction to be made between uncertainty due to a lack of evidence (vacuity) or uncertainty due to the presence of conflicting evidence (dissonance). A multinomial opinion, $\omega$, can be expressed as $\omega=\left(\mathbf{b}, u, \mathbf{a}\right)$, where $\mathbf{b}$ is a belief mass vector, the scalar $u$ is the uncertainty mass and $\mathbf{a}$ is the base rate vector. For an output, $\mathbf{y}$, of dimension K
\begin{equation}
    \mathbf{b}\in\mathbb{R}^K,\quad\mathbf{a}\in\mathbb{R}^K,\quad\mathbf{y}\in\mathbb{R}^K.
\end{equation}
A projection of $\omega$ onto a probability distribution can be made according to
\begin{equation}
    P(y=k) = b_k + a_ku.
\label{eq:prob_projection}
\end{equation}
Given that for the base rate vector $\sum_{k=1}^Ka_k=1$, an additivity requirement is described by
\begin{equation}
    u+\sum_{k=1}^K b_k=1.
\end{equation}
